\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-05 paper/eccv2020/sections/discussion.tex
Fixed typos and changed one sentence in the introduction

In summary, we demonstrate a method to greatly improve depth estimates from
monocular depth estimators by correcting the scale ambiguity errors inherent
with such techniques.  Our approach produces depth maps with accurate absolute
depth, and helps the generalization of neural networks for MDE across scene
types, including on data captured with our hardware prototype.  Moreover, we
require only minimal additional sensing hardware; we show that a single measurement
histogram from a diffused SPAD sensor contains enough information about global
scene geometry to correct errors in monocular depth estimates.

>>>>

In summary, we demonstrate a method to greatly improve depth estimates from
monocular depth estimators by correcting the scale ambiguity errors inherent
with such techniques.  Our approach produces depth maps with accurate absolute
depth, and helps MDE neural networks generalize across scene
types, including on data captured with our hardware prototype.  Moreover, we
require only minimal additional sensing hardware; we show that a single measurement
histogram from a diffused SPAD sensor contains enough information about global
scene geometry to correct errors in monocular depth estimates.

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Fixed typos and changed one sentence in the introduction

Using the hardware prototype, we captured a number of scenes as shown in
Figures~\ref{fig:results_captured},~\ref{fig:captured_diffuse_small}, and in the supplement. We crop the RGB image
to have dimensions that are multiples of 32. For DORN only, we further
downsample the image to a resolution of $353 \times 257$. We then feed this RGB
image into the monocular depth estimation algorithm. In
Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and
processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among
the depth estimators we tested. Additional scenes, also processed with other MDE
approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are
included in the supplement. The ground truth depth is captured with the scanned
SPAD, as described above, and regions with low signal-to-noise ratio are masked
out (shown in black).

>>>>

Using the hardware prototype, we captured a number of scenes as shown in
Figures~\ref{fig:results_captured},~\ref{fig:captured_diffuse_small}, and in the supplement. We crop the RGB image
to have dimensions that are multiples of 32. For DORN only, we further
downsample the image to a resolution of $353 \times 257$. We then feed this RGB
image into the monocular depth estimation algorithm. In
Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and
processed with MiDaS~\cite{Lasinger:2019}, which achieved the best results among
the depth estimators we tested. Additional scenes, also processed with other MDE
approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are
included in the supplement. The ground truth depth is captured with the scanned
SPAD, as described above, and regions with low signal-to-noise ratio are masked
out (shown in black).

### 2020-03-05 paper/eccv2020/sections/introduction.tex
Fixed typos and changed one sentence in the introduction

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. \edit{Moreover, we build an camera prototype that combines an RGB camera and a single-pixel time-resolved detector.}  With this
work, we present a practical way to disambiguate depth estimation with RGB
images using minimal additional sensing hardware. Specifically, we make the
following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram aggregated by a time-resolved detector to address scale ambiguity in MDE.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

>>>>

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. \edit{Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique.} % With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.

In summary, we make the
following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram aggregated by a time-resolved detector to address scale ambiguity in MDE.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

### 2020-03-05 paper/eccv2020/sections/simulation.tex
final pass (hopefully)
Fixed typos and changed one sentence in the introduction

We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
249~training and 215~testing scenes with RGB-D images captured using a Microsoft
Kinect.

@@

\begin{figure*}[t]
  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
  \includegraphics[width=\textwidth]{comparison.pdf}
  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
  \caption{Simulated results from NYU v2 computed with the DenseDepth
  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
  but contain systematic error. Oracle access to the ground truth depth maps,
  either through the median depth or the depth histogram, can remove this error
  and correct the depth maps. \edit{The proposed method uses a single transient measurement} and does not rely on ground truth depth, but it achieves
  a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
  \vspace{-1em}
\end{figure*}

>>>>

We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
249~training and 215~testing RGB-D images captured with a Kinect.

@@

\begin{figure*}[t]
  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
  \includegraphics[width=\textwidth]{comparison.pdf}
  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
  \caption{Simulated results from NYU Depth v2 computed with the DenseDepth
  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
  but contain systematic error. Oracle access to the ground truth depth maps,
  either through the median depth or the depth histogram, can remove this error
  and correct the depth maps. \edit{The proposed method uses a single transient measurement} and does not rely on ground truth depth, but it achieves
  a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
  \vspace{-1em}
\end{figure*}
